---
title: "EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(zoo)
```

# Set correct path

```{r}
#path = "~/Documents/University/WessexWater/wessexwater/"
setwd(path)
getwd()
```

# Load Flow data and Repair Jobs

```{r}
load("../datFlow.rda")
load("../repFlow.rda")
```

# Select a Flow Series & Transform date to Date format

```{r}
myid = "AW008"
df = datFlow %>% 
  filter(id == myid) %>% 
  mutate(date = as.Date(date))
```


# Plot it

```{r}
ggplot(data=df, aes(x=date, y=y)) + 
  geom_point()
```

# Grab repFlow and filter by the same ID. Find start and end dates

```{r}
tmpStart = repFlow %>% 
      filter(id == myid) %>% 
      select(starts_with("Start")) %>% 
      select_if(~ !any(is.na(.))) %>% 
      mutate_all( ~ as.Date(.)) %>% 
      gather
```

```{r}
tmpEnd <- repFlow %>% filter(id == myid) %>% 
                      select(starts_with("End")) %>% 
                      select_if(~ !any(is.na(.))) %>% 
                      mutate_all( ~ as.Date(.)) %>% gather 
```

# Plot all the repair jobs, if there are any

```{r}
pl = ggplot(data=df, aes(x=date, y=y)) + 
  geom_point()
if(nrow(tmpStart)){
 pl <- pl + geom_vline(xintercept = tmpStart$value, col = 3)
}
if(nrow(tmpEnd)){
 pl <- pl + geom_vline(xintercept = tmpEnd$value, col = 2)
}
```

# Compute minimum night flow

```{r}
mnf = df[(9 <= df$tod) & (df$tod <= 21), ] %>% group_by(id, date) %>% summarise(mnf=min(y)) %>% ungroup()
```

# Compute average daily flow
```{r}
adf = df[(9 > df$tod) | (df$tod > 21), ] %>% group_by(id, date) %>% summarise(adf=mean(y)) %>% ungroup()
```

# Rolling average
```{r}
n_days = 7
rolling = data.frame(
  date=as.Date(rollmean(mnf$date, k=n_days)),
  mnf=rollmean(mnf$mnf, k=n_days),
  adf=rollmean(adf$adf, k=n_days)
)
```

# Plot
```{r}
pl = rolling %>% 
  gather(key, value, -date) %>% 
  {ggplot(data=.) + geom_line(aes(x=date, y=value, color=key))}

if(nrow(tmpStart)){
 pl <- pl + geom_vline(xintercept = tmpStart$value, col = 3)
}
if(nrow(tmpEnd)){
 pl <- pl + geom_vline(xintercept = tmpEnd$value, col = 2)
}
```



# Put the series together
```{r}
mnf_adf = mnf %>% mutate(adf=adf$adf)
mnf_adf %>% gather(key, value, -id, -date) %>% 
  {ggplot(data=.) + geom_line(aes(x=date, y=value, color=key))}

```



# New Idea
Clustering. I want to grab a subset of timeseries. For each time series, I want to obtain the ratio between rolling average MNF and rolling average ADF. I call this ratio_rolling. Then I want to cluster these timeseries based on ratio rolling.

### Grab first 50 series

```{r}
series = unique(datFlow$id)[1:50]
```

### grab equivalent data

```{r}
df = datFlow %>% 
  filter(id %in% series)
```

### Decide start of night and end of night
```{r}
night_start = 9     # 2 am
night_end = 21      # 5:30 am 
```

### Calculate MNF & ADF

```{r}
mnf = df %>% filter((night_start <= tod) & (tod <= night_end)) %>% group_by(id, date) %>% summarise(mnf=min(y)) %>% ungroup()
adf = df %>% filter((night_start > tod) | (tod > night_end)) %>% group_by(id, date) %>% summarise(adf=mean(y)) %>% ungroup()
```

### Compute 7 days rolling average for MNF

```{r}
inter_roll <- function(df, n_days=7){
  new <- df %>% 
    mutate(mnf_roll=rollmean(mnf, n_days, na.pad=TRUE)) %>% 
    select(-mnf)
  new$mnf_roll = na.spline(new$mnf_roll, 1:nrow(new))
  return(new)
}
```


```{r}
dfs = mnf %>%
    filter(id == series[1]) %>% 
    mutate(mnf_roll=rollmean(mnf, 7, na.pad=TRUE))
for (ix in 2:50){
  dfs = mnf %>%
  filter(id == series[ix]) %>% 
  mutate(mnf_roll=rollmean(mnf, 7, na.pad=TRUE)) %>% 
  rbind(dfs, .)
}
```





